\section{Background and Related Work}
\label{sec:related}

This section reviews automated test suite generation, multi-agent LLM systems, execution-driven agentic interfaces, and the challenge of compliance bias in repository-level software maintenance.

\subsection{Large Language Models for Automated Test Generation}
Modern automated software testing techniques can be classified based on their inputs and primary operating modes. Regarding inputs, test suites have been derived from source code signatures~\cite{bareiss2022code, schafer2023empirical}, formal program specifications~\cite{docprompting}, semi-structured documentation~\cite{testexplora}, and previous program execution traces~\cite{swebench}. Black-box approaches generate test inputs directly from API specifications or documentation without requiring source code access, whereas white-box approaches analyze program structure to maximize branch and statement coverage~\cite{evosuite, randoop, whiteboxrest2025}.

Recent advancements in Large Language Models (LLMs) have transformed automated test generation from heuristic input fuzzing to semantic test synthesis. Tools such as ChatUnitTest~\cite{xie2023chatunitest} and CODAMOSA~\cite{lemieux2023codamosa} leverage pre-trained code models to generate unit tests, achieving high code coverage on self-contained Java methods. In repository-level contexts, DocPrompting~\cite{docprompting} and RepoBench~\cite{repobench} utilize multi-file context to complete method calls. Recent industrial deployments, such as ByteDance's TestGPT-Server~\cite{testgptserver2025}, demonstrate line coverage gains up to 40.5\% across 14,366 microservice APIs. Additional domain-specific applications include REST API test generation from requirements~\cite{requirements2025}, Postman collections~\cite{postman2024}, and client code for C libraries~\cite{c_libraries2026}. However, all these existing techniques are primarily limited in the types of defects they can detect: they excel at identifying runtime crashes or unhandled exceptions, but struggle to detect logic flaws that go beyond mere syntax.

\subsection{Multi-Agent REST API Testing and Amplification}
Recent efforts have explored multi-agent collaboration and reinforcement learning for API test generation. Frameworks like LlamaRestTest~\cite{llamaresttest2025}, MASTEST~\cite{mastest2025}, and AutoRestTest~\cite{autoresttest2025} combine small language models with multi-agent reinforcement learning (MARL) and semantic predicate dependency graphs (SPDG) to improve operation coverage and status code diversity. RestTSLLM~\cite{resttsllm2025} and ASTRA~\cite{astra2026} integrate test specification languages with API response evaluations to refine test suites iteratively.

Complementary techniques focus on test amplification~\cite{amplification2025}, constraint mining via observation-confirmation schemes~\cite{rbctest2024}, formalizing regulatory compliance requirements~\cite{regulatory2026}, authorization checking in microservices~\cite{authorization2026}, structural similarity analysis~\cite{isdfs2026, jcsse2025}, combinatorial methods~\cite{combinatorial2025}, graph-based prompting~\cite{sose2025}, security taxonomies~\cite{security2025}, functional API testing~\cite{isec2025}, industrial billing systems~\cite{asens2024}, and developer workload reduction~\cite{pulseui2024}. While multi-agent REST testing improves endpoint reachability and response code coverage, these approaches assume structural API specifications (such as OpenAPI/Swagger specs) and do not address repository-level codebases lacking formal API descriptions.

\subsection{Execution-Driven Agents and Dynamic Execution Signals}
Search-Based Software Testing (SBST) tools such as EvoSuite~\cite{evosuite} and Randoop~\cite{randoop} utilize genetic algorithms and random input generation to monitor program execution dynamically. While SBST tools excel at discovering edge-case crashes by executing code paths, they lack natural language understanding, producing unreadable test assertions with high false-positive rates~\cite{siddiq2023exploratory}.

To bridge the gap between high-level semantic reasoning and dynamic execution, recent work introduced agent-computer interfaces. SWE-agent~\cite{sweagent} equipped LLMs with interactive bash shell environments, enabling autonomous file navigation, tool execution, and real-time execution feedback for repository-level software engineering tasks. While SWE-agent proved effective for automated bug fixing on SWE-bench~\cite{sweagent}, its application to proactive test suite generation, intent-driven assertion refinement, and compliance bias mitigation remains unexplored.

\subsection{Compliance Bias and Oracle Generation Constraints}
A common limitation of static LLM-based test generators is their vulnerability to \textit{compliance bias}~\cite{testexplora}. Because static models generate test code in a single inference pass without execution signals, they exhibit a passive tendency to conform to existing code implementations. Automated oracle generators, such as AGORA+~\cite{agoraplus2025} and LRASGen~\cite{lrasgen2026}, attempt to learn invariants or generate specifications from source code, but remain susceptible to static concretion traps.

When evaluated on defective repositories, static generators produce unit tests that syntactically conform to the buggy code, yielding a Fail-to-Pass (F2P) rate floor of only 16.06\% on the TestExplora benchmark~\cite{testexplora}. To the best of our knowledge, ours is the first approach for automated repository-level test suite generation that integrates interactive terminal execution feedback to dynamically reject compliance assumptions.

\nocite{*}
