\section{Threats to Validity}
\label{sec:threats}

In this section, we discuss potential threats to the validity of our empirical study and describe the specific mitigation strategies implemented during our experiment.

\subsection{Internal Validity}
\begin{itemize}
    \item \textbf{LLM Stochasticity and Network Disruption:} Temperature sampling randomness and intermittent OpenRouter API disruptions (HTTP 429 rate limits, HTTP 503 server overloads, 30-second network timeouts) could introduce non-deterministic execution failures. We mitigated this threat by fixing model temperatures to $\text{temperature}=0.0$, implementing an exponential backoff retry mechanism with randomized jitter ($t_{\text{wait}} = 2^{\text{attempt}} + \text{Uniform}(0, 1)$ seconds, up to 5 retries), and averaging results across $K=3$ independent sampling runs.
    \item \textbf{Prompt Consistency:} Differences in system prompts across agent roles could introduce unobserved prompt engineering bias. We mitigated this by holding system prompts strictly constant across all $4,656$ agent executions and enforcing zero temperature during inference.
\end{itemize}

\subsection{External Validity}
\begin{itemize}
    \item \textbf{Generalizability Across Programming Languages:} Our evaluation focused exclusively on Python repositories within the TestExplora benchmark, which may limit generalizability to statically typed compiled languages (e.g., Java, C++). We mitigated this by selecting $N=1,552$ diverse tasks spanning 482 distinct open-source repositories across 10 broad software domain categories (web frameworks, database engines, data science, infrastructure monitoring).
    \item \textbf{Model Specificity:} Experimental findings might be tied to specific LLM choices (DeepSeek-V3 and Llama-3.3-70B). We mitigated this by evaluating open-access, state-of-the-art weights via OpenRouter rather than proprietary closed models, ensuring open replication.
\end{itemize}

\subsection{Construct Validity}
\begin{itemize}
    \item \textbf{Accuracy of Intent-Derived Test Oracles:} Measuring test suite quality via automated metrics could misrepresent human developer intent. We mitigated this by adopting the Fail-to-Pass (F2P) rate metric validated by Microsoft TestExplora's automated \textit{DocAgent} oracle, which strictly evaluates whether candidate tests fail on defective code and pass on fixed implementations.
\end{itemize}

\subsection{Conclusion Validity}
\begin{itemize}
    \item \textbf{Statistical Power and Non-Normal Dispersion:} Applying parametric statistical tests to skewed repository-level F2P distributions could inflate Type I error rates. We mitigated this by utilizing non-parametric paired one-tailed Wilcoxon signed-rank tests ($W$) at the repository observation level ($N_{\text{obs}} = 1,311$) alongside Cliff's Delta ($\delta$) effect size measurements, avoiding parametric normality assumptions.
\end{itemize}
